DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving

### 2017-11-13 paper/cvpr2018/cvpr2018_draft.tex
paper writing: dataset collection'

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{subcaption}
%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small TODO: Pull figure caption goes here.}}
        \label{fig:response_map}
\end{figure}
\textbf{\emph{3. Why is it hard? (E.g. why do naive approaches fail?)}}

@@

\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving to robustly track a car. The proposed framework greatly enhanced the trackers' robustness by updating tracker's target representation, in the meanwhile solving the problem of instance association between frames.

\item We design various temporal model for the problems of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.

\item We demonstrate the effectiveness of using ``privileged information" further boost the prediction accuracy. [NOT DONE].

@@

%%% TY: write related work for object detection, segmentation, instance segmentation
\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%%% DW: write related work for visual tracking
%%% DW: write related dataset for autonoumous driving

@@

%% DW: (1)traditional segmentic segmentation dataset
%% DW: (2) synthetic dataset
%% DW: (3) temporal consistent dataset

@@

%%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
\textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}

@@

~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.

@@

\subsection{traffic participants detection}

\subsection{instance tracking}

\subsection{trajectory prediction}

@@

Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups. The major features of collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).

There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map. In our experiment, we used only left front camera view data.
The focus of this paper is on car trajectory prediction on high ways. We list our logic for collecting continuous car tracking in List~\ref{Dataset_collection}. (TODO: make a list).
Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).

\begin{algorithm}
\caption{Multimodal Deep Dynamic Networks -- training}\label{Dataset_collection}
\LinesNumbered
\SetAlgoLined
\SetAlgoNoEnd
\DontPrintSemicolon
\SetKwFunction{zeroes}{zeroes}
\KwData{\;
          $ \mathbf{X^1=\{ x^1_i\}_{i \in [1 \ldots t]}}$ - raw input(skeletal) feature sequence.\;
          $ \mathbf{X^2=\{ x^2_i\}_{i \in [1 \ldots t]}}$ - raw input(depth) feature sequence in the form of \;
          \hspace{1cm}$M_1 \times M_2 \times T$, where $M_1, M_2$ are the height and width of the input \;
          \hspace{1cm}  image and $T$ is the number of contiguous frames of the \;
          \hspace{1cm} spatio-temporal cuboid. \;
          \hspace{1cm}  {\scriptsize{}Note that the GPU library \emph{cuda-convnet}~\cite{krizhevsky2012imagenet} used requires square size images and $T$ is a multiple of $4$}.\;
          $ \mathbf{Y=\{ y_i\}_{i \in [1 \ldots t]}}$  - frame based local label (achieved by semi-supervised \; \hspace{1cm} forced-aligment), \;
          \hspace{1cm}  where $ \mathbf{y_i} \in \{ C * S + \textbf{\emph{1}} \} $ with $C$ is the number of class, $S$ is the  \;
          \hspace{1cm}  number of hidden states for each class, $\textbf{\emph{1}}$ as ergodic state.
            }
\For{$m \leftarrow 1$ to $2$}{
    \SetAlgoVlined
    \eIf{$m$ is $1$}{
        Preprocessing the dataCordts2016Cityscapes $ \mathbf{X^1}$ as in Eq.\ref{sk_features}.\;
        Normalizing(zero mean, unit variance per dimension) the above features and feed to to Eq.\ref{GRBMenergy}. \;
        Pre-training the networks using \emph{Contrastive Divergence}. \;
        Supervised fine-tuning the Deep Belief Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} backpropagation.\;
    }{
        Preprocessing the data $ \mathbf{X^2}$ (normalizing, median filtering the depth data) Algo.\ref{normalization_scheme_1} or Algo.\ref{normalization_scheme_2}.\;
        Feeding the above features to Eq.\ref{ReLU}. \;
        Supervised fine-tuning the Deep 3D Convolutional Neural Networks using $ \mathbf{Y}$ by standard mini-batch \emph{SGD} Backpropagation.\;
    }
}
\KwResult{\;
        $\mathbf{GDBN}$ - a gaussian bernoulli visible layer Deep Belief Network to \;
                \hspace{1cm} generate the emission probabilities for hidden markov model.\;
        $\mathbf{3DCNN}$ - a 3D Deep Convolutional Neural Networks to generate the\;
                \hspace{1cm}   emission probabilities for hidden markov model.\;
        $\mathbf{p(H_1)}$ - prior probability for $ \mathbf{Y}$.\;
        $ \mathbf{p(H_t | H_{t-1})}$ - transition probability for $ \mathbf{Y}$,  enforcing the beginning and \;
                    \hspace{1cm} ending of a sequence can only start from the first or the last state.
}
\end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Implementations}

@@

We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
We use the pretrained detection network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA. Curretnly

A comprehensive survey of speed/accuracy trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer the keen readers to

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation}

@@

    \caption{ {\small
          Baseline comparisons with arrows indicating performance changes comparing with the upper row parallel experiment.
          First two rows investigate the impact of projecting deep features into a kernel space \emph{vs.} using linear deep features.
          Next two rows compare the traditional using max location \emph{vs.} the proposed multi-resolution convnets paradigm for decoding target translational movement.
          Last two rows illustrate the benefit of adaptive learning rate through time (with scale update). }
          } \label{table_baseline}
\end{table}

@@

    \caption{ {\small
          Comparison with the most recent methods }
          } \label{table_baseline2}
\end{table}
\section{Conclusions}

@@

\section*{Details of the Code}

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
 \pdfoutput=1
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{subcaption}
%\usepackage{slashbox}
\usepackage{color}
\usepackage[english]{babel}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmic}

\DeclareCaptionLabelFormat{noname}{#2}
\captionsetup[algorithm]{labelformat=noname}

\newlength\myindent
\setlength\myindent{2em}
\newcommand\bindent[1][\myindent]{%
  \begingroup
  \setlength{\itemindent}{#1}
  \addtolength{\algorithmicindent}{#1}
}
\newcommand\eindent{\endgroup}

\usepackage{multirow}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small TODO: Pull figure caption goes here.}}
        \label{fig:pull_figure}
\end{figure}
\textbf{\emph{3. Why is it hard? (E.g. why do naive approaches fail?)}}

@@

\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving for robustly vehicle tracking. The proposed framework greatly enhanced the trackers' robustness by updating tracker's target representation, in the meanwhile solving the problem of instance association between frames.

\item We design various temporal models for the problem of predicting future trajectories based on historical data and show that the temporal model generating intermediate output utilising the whole historical data performs better than the frame-to-frame based output temporal model.

\item We demonstrate the effectiveness of using ``privileged information"(e.g., scene semantics and car pose information) further boost the prediction accuracy. [NOT DONE YET].

@@

%%% TY: write related work for object detection, segmentation, instance segmentation
\textbf{\emph{1. Object detection, segmentation, instance segmentation}}

TODO: TY
%%% DW: write related work for visual tracking
%%% DW: write related dataset for autonoumous driving

@@

TODO: DW
%% DW: (1)traditional segmentic segmentation dataset
%% DW: (2) synthetic dataset
%% DW: (3) temporal consistent dataset

@@

%%% ZN: write related works for Recurrent Networks (used in the context of autonomous driving)
\begin{figure*}[t]
        \centering
        \includegraphics[width=0.75\textwidth]{figures/framework.pdf}
        \caption{ {\small TODO: framework caption goes here.}}
        \label{fig:framework}
\end{figure*}

\textbf{\emph{4. Recurrent Networks (used in the context of autonomous driving)}}

@@

TODO: cite below papers;
~\cite{xu2017end}: End-to-end learning of driving models from large-scale video dataset.

@@

We first describe our overall approach for car trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
Our goal is via collecting the visual information from the past to predict the traffic participants future trajectory. Fig.~\ref{fig:framework} shows the overall architecture of our proposed framework.

\subsection{Traffic Participants detection}

\subsection{Instance tracking}

We compare two state-of-the-art trackers (given the time vs. accuracy) of the trackers.
\begin{figure}[t]
        \centering
        \includegraphics[width=0.4\textwidth]{figures/double_detection.png}
        \caption{ {\small TODO: Instance association caption goes here.}}
        \label{fig:Instance_associationn}
\end{figure}

\subsection{Semantic segmentation}
We use the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated}.

\subsection{Trajectory prediction}

@@

Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups. The major features of collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map. In our experiment, we used only left front camera view data.

The focus of this paper is on car trajectory prediction on high ways which corresponds to sequence number 1 in the SYNTHIA dataset. We especially concern about the cars that are relatively close to the driver. Hence, we start tracking the vehicle when the vehicle's pixel occupancy rate \emph{(POR)} is larger than 0.2\% and stop tracking the instance when the POR is smaller than 0.1\%. The POR of 0.2\% and 0.1\% correspond to roughly 30 and 50 meters of relative distance between the driver and tracking vehicle so as to suffice the safety distance for drivers to make timely reaction.
We follow the traditional paradigm for tracking to collect target's bounding box: $[x, y, w, h]$ of each frame. Moreover, the minimum relative distance $d_{min}$ and maximum relative distance $d_{max}$ can also be acquired from the depth camera.
We list our logic for collecting continuous car tracking in List~\ref{list:dataset_collection}. 
Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).

TODO: generate a table for total number of frames and sequence tracklets!

\begin{algorithm}[h]
\begin{algorithmic}
\caption{\textbf{Dataset ground truth construction}}\label{list:dataset_collection}
\STATE \textbf{Step 1} $\rightarrow $ get traffic participants from ground truth annotation with only cars as instances.
\STATE \textbf{Step 2} {$\rightarrow $ { 
\bindent
  \IF{POR $> 0.2\%$}
    %\bindent[1.45cm]
    \STATE $\Rightarrow$ start tracking instance , 
    \STATE $\Rightarrow$ collecting 3D tracking rectangular: $[x, y, w, h, d_{min}, d_{max}]$
    \STATE $\Rightarrow$ collecting semantic segmentation image, $I_{seg}$.
    \STATE $\Rightarrow$ collecting 2d car pose from RGB input $I_{car}$.
    %\eindent
  \ELSIF{POR $< 0.1\%$}
    \STATE $\Rightarrow$ stop tracking 
    \ENDIF\eindent}
  }
\STATE \textbf{Step 3} $\rightarrow $ split sequences into tracklets of 23 frames:
{\bindent
    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input
    \STATE $\Rightarrow$  next 8 frames (1.6 sec) as the held-up future trajectory to be predicted.
\eindent}    
\end{algorithmic}
\end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Implementations}\label{sec:Implementations}

@@

We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
We use the pretrained network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA with two classes: cars \emph{v.s.} background.
A comprehensive survey of trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer keen readers to the aforementioned paper for a more complete comparison to achieve the right speed/memeory/accuracy balance for a given application and platform.

As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small object, it's very competitive for detecting larger objects. In this paper, we concerns mostly about cars that are closer to the driver. Hence, we chose the POR as 0.2\% which favors detectors that are robust in larger object detection. 
Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when the objects of interest are large.

\begin{table*}\centering
\ra{1.}
\begin{tabular}{@{}llllllllllll@{}}\toprule
\multicolumn{2}{c}{conf}  & 0.5  & 0.55 & 0.6 &  0.65 & 0.7  & 0.75 & 0.8 &  0.85 & 0.9  & 0.95\\
\hline
\multirow{3}{*}{SSD}&   precision & \textbf{92.0 } & 91.8 & 91.7 & 91.4 & 91.1 & 91.0 & 90.5 & 90.2 & 89.4 & 87.4\\
                    &    recall   & \textbf{92.3}  & 92.1 & 92.0 & 91.8 & 91.4 & 91.3 & 90.8 & 90.5 & 89.7 & 87.7\\
                    &    f-score  & \textbf{92.2 } & 92.0 & 91.8 & 91.6 & 91.3 & 91.1 & 91.1 & 90.4 & 89.6 & 87.6\\
\multirow{3}{*}{Faster-RCNN}
                    &   precision & 81.2  & 81.2  & 81.1 & 81.1 & 81.1 & 81.0 & 81.0 & 80.7 & 80.5 & 80.0 \\
                    &   recall    & 91.4  & 91.4  & 91.3 & 91.3 & 91.3 & 91.3 & 91.3 & 90.9 & 90.7 & 90.2\\
                    &   f-score   & 86.0  & 86.0  & 86.0 & 86.0 & 86.0 & 86.0 & 86.0 & 85.5 & 85.3 & 84.8\\
\bottomrule
\end{tabular}
\caption{Caption: TODO results: (1) SSD better at detecting large object(which is in our case). (2) Faster-RCNN  is more robust to confidence threshold}
\label{tab:ssd_fasterrcnn}
\end{table*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Evaluation}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
        \caption{ {\small TODO: evaluation caption goes here.}}
        \label{fig:evaluation}
\end{figure}

@@

    \caption{ {\small
         TODO: this table is just a place holder, currently has no meaning.}
          } \label{table_baseline}
\end{table}

@@

    \caption{ {\small
    TODO: this table is just a place holder, currently has no meaning. WZN will update the numbers
          Comparison with the most recent methods }
          } \label{table_baseline2}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evaluation Metrics}

\section{Conclusions}

@@

\section*{Details of the Code}
 The code will be made public alongside the publication.
